That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b

### 2019-01-23 ms.tex
start discussion

@@

%For more direct comparison with \citep{teachey18b}, we also considered a second systematics model that included three terms: (1) a visit-long second order polynomial trend in time, and (2) a constant offset after orbit 14.
%We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend. A long-term trend was favored by the \cite{teachey18b} analysis, and has been observed in other long-duration WFC3 time series \citep[e.g.][]{stevenson14, kreidberg18b}. The model is:
%\begin{equation}
%S_{2,i} = c_{j} \times (1 + vt_i + v_2t_i^2)
%\end{equation}
%where $v$ and $v_2$ are free parameters and $t_i$ is the time elapsed since the first exposure in the visit.

@@

\subsection{Comparison with Teachey \& Kipping (2018)}
\cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the results findings here.  To make a direct comparison with their results, we fit the raw TK18 data directly.

@@

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig5_pairs.pdf}
    \caption{Posterior distributions for the moon radius and time of central transit. Blue = this work; red = our analysis of TK18 data.}
\label{fig:corner}
\end{figure}

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig6_rawdata.pdf}
    \caption{Comparison of raw data.}
\label{fig:raw}
\end{figure}

\section{Discussion and Conclusion}
We found
approach to data reduction was very similar, but of the data reduction, and

\acknowledgments
Dan Foreman-Mackey

The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.

>>>>

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig6_rawdata.pdf}
    \caption{Top: raw data from this work (blue) compared to TK18 (red). Bottom: the difference in raw photoelectron counts between the data sets. The moon ingress identified by TK18 is marked by the dotted gray line.}
\label{fig:raw}
\end{figure}

@@

@@

\subsection{Comparison with Teachey \& Kipping (2018)}
\cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.  To make a direct comparison with their results, we fit the raw TK18 data directly.

@@

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig5_pairs.pdf}
    \caption{Posterior distributions for the moon radius and time of transit based on an MCMC fit to data from this work (blue) and from TK18 (red). The shading corresponds to $1-$, $2-$, and $3\sigma$ contours (darkest to lightest). These values are marginalized over all other model parameters. The diagonal shows the normalized posterior probability density.}
\label{fig:corner}
\end{figure}

\section{Conclusion}
In this work, we presented an independent analysis of HST observations of the Kepler-1625 system. In contrast to previous analysis by \citep{teachey18b}, we do not find evidence for the transit of a moon.

what is 
approach to data reduction was very similar, but of the data reduction, and

\acknowledgments
The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.
